DraftOne

### 2017-03-21 writing/DraftOne.Rmd
power_calc - What even??

##2nd attempt at power_calc

@@

#Example that doesn't work: 
power_calc(varying = "n", values = c(5, 10, 25), n_reps = 3, central = 100, sd=10, exposure_type = "continuous", exposure_trend = "cos1", exposure_amp = .6, average_outcome=22, outcome_trend = "no trend", outcome_amp = .6, rr=1.1, start.date = "2000-01-01")
```

>>>>

##2nd attempt at power_calc using purrr

@@

#Example that doesn't work: 
power_calc(varying = "n", values = c(5, 10, 25), n_reps = 3, central = 100, sd=10, exposure_type = "continuous", exposure_trend = "cos1", exposure_amp = .6, average_outcome=22, outcome_trend = "no trend", outcome_amp = .6, rr=1.1, start.date = "2000-01-01", model = "spline", df_year = 1)
```

Not working, so step by step breakdown:

```{r}
#Establishing values for arguments
varying = "n"
values = c(5, 10, 25)
n_reps = 3
central = 100
sd=10
exposure_type = "continuous"
exposure_trend = "cos1"
exposure_amp = .6
average_outcome=22
outcome_trend = "no trend"
outcome_amp = .6
rr=1.1
start.date = "2000-01-01"
model = "spline"
df_year = 1

n<- c(5, 10, 20)

#Getting list of data frames with date, x, outcome for each run
rep_df <- n %>% map(create_sims, n_reps=n_reps, central=central, sd=sd, 
                        exposure_type=exposure_type,
                        exposure_trend=exposure_trend,exposure_amp=exposure_amp,
                        average_outcome=average_outcome,outcome_trend=outcome_trend,
                        outcome_amp = outcome_amp, rr=rr, start.date = start.date)
rep_df

#Try with actual values:

rep_df <- n %>% map(create_sims, n_reps=3, central=100, sd=10, 
                        exposure_type = "continuous",
                        exposure_trend= "cos1",exposure_amp=.6,
                        average_outcome=22,outcome_trend="no trend",
                        outcome_amp = .6, rr=1.1, start.date = "2000-01-01")
rep_df
#This works, but why are the outcomes crazy? Oh noooooooo :( 
```
